Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-01-08 paper/ms.tex
Even more on Carlyn's paper.
Added a revised figure from Carlyn

Other groups have simulated explosions from hybrid progenitors. 
\citet{kromeretal2015} performed pure deflagration simulations from models 
with a C core. They found that their models may explain some faint events 
such as SN 2008ha~\citep{foleyetal2009}.
\citet{bravoetal2016} performed one-dimensional simulations of explosions from 
a variety of progenitor models assuming both pure deflagration and the DDT 
explosion mechanism. 
Some of their models are similar to those of \citep{denissenkovetal2015} and 
they report that many models produce less synthesized
\Ni{56}, indicating dimmer events. They also note that some of their
models may explain Iax events.

\citet{willcoxetal2016} simulated explosions from the progenitors of 
\citep{denissenkovetal2015} and

Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass.png}
\caption{\label{fig:compare}
SAME AS DON'S FIGURE 19.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}

>>>>

Other groups have simulated explosions from hybrid progenitors. 
\citet{kromeretal2015} performed pure deflagration simulations from models 
with a C core. They found that their models may explain some faint events 
such as SN 2008ha~\citep{foleyetal2009}.
\citet{bravoetal2016} performed one-dimensional simulations of explosions from 
a variety of progenitor models assuming both pure deflagration and the DDT 
explosion mechanism. 
Some of their models are similar to those of \citep{denissenkovetal2015} and 
they report that many models produce less synthesized
\Ni{56}, indicating dimmer events. They also note that some of their
models may explain Iax events.
\citet{willcoxetal2016} simulated explosions from the progenitors of 
\citep{denissenkovetal2015} and found a trend of lower energy and lower
\Ni{56} yield when compared to explosions from traditional C/O progenitors.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare}
SAME AS DON'S FIGURE 19.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}
